### 2014-10-17 simulation.Rmd
gh-27: Adding a results-combining rscript step.

*Invocation:*
```{r, echo=FALSE}
library(pander)
# library(ggplot2)
panderOptions("table.split.table", Inf)  # Let tables become arbitrarily wide rather than wrapping.
source("context-inference-fns.R")
top_n_bottom <- function(df, k) { # Take the top and bottom k rows
    n = nrow(df)
    if(2*k < n) {
        df[c(1:k,(n-(k-1)):n), ]
    }
    else {
        df
    }
}
counts_table <- function(in_longwin, in_shortwin, half_n_show) {
    if ( in_longwin > longwin(model@counts) || in_shortwin > shortwin(model@counts) ) {
        cat("Window size of counts too small.")
    }
    else {
        resids = computeresids(model,
                in_longwin=in_longwin,
                in_shortwin=in_shortwin,
                in_leftwin=in_shortwin,
                counts=model@counts)
        pandoc.table(top_n_bottom(resids, half_n_show), style="rmarkdown")
    }
}
cat(model@invocation)
```

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
par_df = data.frame(value = model@results[["par"]], row.names = names(model@results[["par"]]))
pandoc.table(par_df, style="rmarkdown")
par_df$names = row.names(par_df)
par_df = par_df[grep("->", par_df$names),]
plot(1:2,type='n',xaxt='n',yaxt='n',bty='n',xlab='',ylab='')
par(mar=c(max(strwidth(par_df$names))/(0.75*strheight("A")),3,1,1)+.1, new=TRUE)
barplot( par_df$value, space=0.2 )
axis(1, at=(1:nrow(par_df))*1.2-0.6, las=3, labels=par_df$names)
plot(1:2,type='n',xaxt='n',yaxt='n',bty='n',xlab='',ylab='')
par(mar=c(max(strwidth(par_df$names))/(0.75*strheight("A")),3,1,1)+.1, new=TRUE)
barplot( par_df$value, log='y', space=0.2 )
axis(1, at=(1:nrow(par_df))*1.2-0.6, las=3, labels=par_df$names)
# ggplot(par_df, aes(x = names, y = value)) +
#     geom_bar(stat = "identity", fill="white", color="gray") +
#     theme(axis.text.x = element_text(angle = 90))
```

>>>>

*Invocation:*
```{r, echo=FALSE}
library(pander)
library(ggplot2)
panderOptions("table.split.table", Inf)  # Let tables become arbitrarily wide rather than wrapping.
source("context-inference-fns.R")
top_n_bottom <- function(df, k) { # Take the top and bottom k rows
    n = nrow(df)
    if(2*k < n) {
        df[c(1:k,(n-(k-1)):n), ]
    }
    else {
        df
    }
}
counts_table <- function(in_longwin, in_shortwin, half_n_show) {
    if ( in_longwin > longwin(model@counts) || in_shortwin > shortwin(model@counts) ) {
        cat("Window size of counts too small.")
    }
    else {
        resids = computeresids(model,
                in_longwin=in_longwin,
                in_shortwin=in_shortwin,
                in_leftwin=in_shortwin,
                counts=model@counts)
        pandoc.table(top_n_bottom(resids, half_n_show), style="rmarkdown")
    }
}
cat(model@invocation)
```

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
par_df = data.frame(value = model@results[["par"]], row.names = names(model@results[["par"]]))
pandoc.table(par_df, style="rmarkdown")
par_df$names = row.names(par_df)
par_df = par_df[grep("->", par_df$names),]
ggplot(par_df, aes(x = names, y = value)) +
    geom_bar(stat = "identity", fill="white", color="gray") +
    theme(axis.text.x = element_text(angle = 90))
```

```{r}
model
```
